---
title: "How to run the IPACS model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to run the IPACS model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Set up
You can install the development version of ipacs from GitHub with `devtools::install_github("amyheather/ipacs")`. You will first need to install devtools, if not already installed. Then, load the ipacs package using `library()`.
```{r library}
library(ipacs)
```

Set value for objects that you may wish to change. In this example, `system.file()` is used to find example data stored in the IPACS package. However, you can input a string with the path to your desired file - e.g. `import_file("myfile.xlsx").
``` {r set_param}
# String with file path for excel sheet with model inputs
input_filename <- system.file("extdata", "IPACS_20230214_fix.xlsx", package="ipacs")
# Method for estimation of mu and sigma (for calculate_mu_sigma())
est_method <- 1
# Standard deviation for length of stay
sd_los <- 3
# Number of runs for each simulation
nruns <- as.integer(5)
# Standard deviation for initial service/visit rate (ISR/IVR)
sd_isr <- 0.5
# Standard deviation for end service rate/final visit rate (ESR/FVR)
sd_esr <- 0.5
# Temporary seed
temp_seed <- 1
# Warmup length
warmup <- 0
```

Use `import_file` to import sheets from file containing model parameters. This will produce 5 dataframes: "arrivals_all", "init_conds", "capacity", "losA" and "costs". As R cannot return multiple objects, we return a list of dataframes and a list of dataframe names, then use assign to create those in our current environment.
```{r import}
files <- import_file(input_filename)
for (x in seq_along(files[[1]])){
  assign(files[[1]][x], files[[2]][[x]])
}
```

Use `calculate_mu_sigma` to recalculate mu and sigma in losA dataframe using your chosen method and sd_los (if applicable).  
``` {r mu_sigma}
losA <- calculate_mu_sigma()
```

Set simulation length to the number of unique dates in arrivals.
``` {r sim_length}
sim_length <- as.integer(length(unique(arrivals_all$date)))
```

Use `create_scenarios` to create scenarios and arr_scenarios.
``` {r scenarios}
scenarios <- create_scenarios(scenarios=TRUE)
arr_scenarios <- create_scenarios(scenarios=FALSE)
```

### Visit-based simulation (P1)
Use `sim_setup` to create objects for visit-based simulation. These are returned in a list, so use assign to extract and add to environment.
``` {r setup_visit}
setup_visit <- sim_setup("visit")
for (i in seq_along(setup_visit[[1]])){
  assign(setup_visit[[1]][i], setup_visit[[2]][[i]])
}
```

Create objects with initial service rate (ISR), end service rate (ESR), and their standard deviations (SD). The SD objects are lists that repeat the SD for the number of visit scenarios.
``` {r isr_esr}
isr <- as.integer(scenarios_visit$IVR)
end_sr <- as.integer(scenarios_visit$FVR)
sd_isr <- as.double(rep(sd_isr, nrow(scenarios_visit)))
sd_esr <- as.double(rep(sd_esr, nrow(scenarios_visit)))
```

Create n_slots, the number of visit slots available per day. This is based on an average visit rate (as from mean of isr and end_sr) multiplied by the capacity for P1 (cap_visit)
``` {r n_slots}
n_slots  <- cap_visit * mean(c(isr, end_sr))
```

Create object to store outputs from each scenario
``` {r null_output}
visits_based_output <- NULL
visits_based_output_q <- NULL
```
