---
title: "How to run the IPACS model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to run the IPACS model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Set up
You can install the development version of ipacs from GitHub with `devtools::install_github("amyheather/ipacs")`. You will first need to install devtools, if not already installed. Then, load the ipacs package using `library()`.
```{r library}
library(ipacs)
```

Set value for objects that you may wish to change. In this example, `system.file()` is used to find example data stored in the IPACS package. However, you can input a string with the path to your desired file - e.g. `import_file("myfile.xlsx").
``` {r set_param}
# String with file path for excel sheet with model inputs
input_filename <- system.file("extdata", "IPACS_20230214_fix.xlsx", package="ipacs")

# Path to save output files to
visit_filename <- "../inst/extdata/visit_output_using_IPACS_20230214_fix.csv"
visit_stoch_filename <- "../inst/extdata/stochastic_visit_output_using_IPACS_20230214_fix.csv"

# Method for estimation of mu and sigma (for calculate_mu_sigma())
est_method <- 1

# Standard deviation for length of stay
sd_los <- 3

# Number of runs for each simulation
nruns <- 5

# Standard deviation for initial service/visit rate (ISR/IVR) and end service
# rate/final visit rate (ESR/FVR)
sd_isr <- 0.5
sd_esr <- 0.5

# Temporary seed
temp_seed <- 1

# Warmup length
warmup <- 0
```

Use [`import_file`](https://amyheather.github.io/ipacs/reference/import_file.html) to import sheets from file containing model parameters. This will produce 5 dataframes: "arrivals_all", "init_conds", "capacity", "losA" and "costs". As R cannot return multiple objects, we return a list of dataframes and a list of dataframe names, then use assign to create those in our current environment.
```{r import}
files <- import_file(input_filename)
for (x in seq_along(files[[1]])){
  assign(files[[1]][x], files[[2]][[x]])
}
```

Use [`calculate_mu_sigma`](https://amyheather.github.io/ipacs/reference/calculate_mu_sigma.html) to recalculate mu and sigma in losA dataframe using your chosen method and sd_los (if applicable).  
``` {r mu_sigma}
losA <- calculate_mu_sigma()
```

Use [`create_scenarios`](https://amyheather.github.io/ipacs/reference/create_scenarios.html) to create scenarios and arr_scenarios.
``` {r scenarios}
scenarios <- create_scenarios(scenarios=TRUE)
arr_scenarios <- create_scenarios(scenarios=FALSE)
```

### Visit-based simulation (P1)
**Set-up:** Use [`sim_setup`](https://amyheather.github.io/ipacs/reference/sim_setup.html) to create objects for visit-based simulation. These are returned in a list, so use assign to extract and add to environment.
``` {r setup_visit}
setup_visit <- sim_setup("visit")
for (i in seq_along(setup_visit[[1]])){
  assign(setup_visit[[1]][i], setup_visit[[2]][[i]])
}
```

**Run simulation:** Use [`run_visit_sim`](https://amyheather.github.io/ipacs/reference/run_visit_sim.html) to run the visit-based simulation. Extract the results (as returned as list).
``` {r run_visit, message = FALSE}
visit_sim_result <- run_visit_sim()
visits_based_output <- visit_sim_result[[1]]
visits_based_output_q <- visit_sim_result[[2]]
```

**Save results:** Use [`save_visit()`](https://amyheather.github.io/ipacs/reference/save_visit.html) extract results for each date for number in queue, occupancy, wait and costs and then save to csv. Use [`save_visit_stoch()`](https://amyheather.github.io/ipacs/reference/save_visit_stoch.html) to correct date formatting and then save the quantiles to csv for optional stochastic report, saving in long format for plotting.
``` {r output_visit}
save_visit(visit_filename)
save_visit_stoch(visit_stoch_filename)
```

### Testing
Checks that output from simulations matchs outputs from IPACS_MODEL repository.
``` {r visit_test}
test_visit <- read.csv("../inst/extdata/visit_testing_using_IPACS_20230214_fix.csv")
new_visit <- read.csv("../inst/extdata/visit_output_using_IPACS_20230214_fix.csv")
print(diffdf::diffdf(new_visit, test_visit))
```
